Spatial phylogenetics of Japanese ferns: Patterns, processes, and implications for conservation

### 2022-01-22 ms/data_readme.Rmd
Update READMEs to use gittargets

Recommended citation for the data: Nitta JH, Mishler BD, Iwasaki W, Ebihara A
(2021) Data from: Spatial phylogenetics of Japanese ferns: Patterns, processes,
and implications for conservation FIXME: add DOI when available

Citation for and links to publications that cite or use the data: Nitta JH,
Mishler BD, Iwasaki W, Ebihara A (2021) Spatial phylogenetics of Japanese ferns:
Patterns, processes, and implications for conservation FIXME: add journal when published

@@

- _targets.tar.gz: Tarball (compressed folder) including all workflow results produced by R targets package
- japan_climate.gpkg: Climate data in Japan downloaded from WorldClim database
- japan_deer_range.gpkg: Distribution maps of Japanese deer (Cervus nippon) in Japan
- japan_ferns_comm_full.csv: Community matrix (species x sites matrix) of native, non-hybrid ferns in Japan, full (unfiltered) dataset
- japan_ferns_inext_results.csv: Results of collection curve analysis on fern specimens in Japan
- japan_ferns_occ_summary.csv: Summary of specimen data of native, non-hybrid ferns in Japan
- japan_ferns_redundancy_by_res: Taxonomic richness, abundance, and redunancy at different spatial resolutions for native, non-hybrid ferns of Japan
- japan_ferns_shape_full.gpkg: Location of grid-cells (sites) for native, non-hybrid ferns in Japan, full (unfiltered) dataset
- japan_ferns_traits_lucid.csv: Morphological trait data of native, non-hybrid ferns in Japan
- japan_map_points.csv: Latitude and longitude of points used to produce a labeled map of Japan
- japan_map.gpkg: Map of Japan
- japan_protected_areas.gpkg: Protected areas in Japan
- testo_sundue_2016_calibrations.csv: Fossil calibration points used for phylogenetic dating analysis
- results.zip: Selected analysis results. Files include:
  - japan_ferns_biodiv.csv: Biodiversity statistics of native, non-hybrid ferns in Japan
  - japan_ferns_comm.csv: Community matrix (species x sites matrix) of native, non-hybrid ferns in Japan used for biodiversity analysis
  - japan_ferns_shape.gpkg: Location of grid-cells (sites) for native, non-hybrid ferns in Japan used for biodiversity analysis
  - japan_ferns_traits.csv: Trait matrix of native, non-hybrid ferns in Japan used for functional biodiversity analysis
  - japan_ferns_tree_dated.tre: Maximim-likelihood, ultrametric (dated) phylogeny of native, non-hybrid ferns in Japan with clades consisting of identical OTUs collapsed to polytomies
  - japan_ferns_tree_uncollapsed.tre: Maximim-likelihood, ultrametric (dated) phylogeny of native, non-hybrid ferns in Japan with clades consisting of identical OTUs not collapsed
  - japan_ferns_tree.tre: Maximim-likelihood phylogeny of native, non-hybrid ferns in Japan

@@

For full methods, see Nitta JH, Mishler BD, Iwasaki W, Ebihara A (2021) Spatial
phylogenetics of Japanese ferns: Patterns, processes, and implications for
conservation FIXME: Add journal when published

@@

_targets.tar.gz: Tarball (compressed folder) including all workflow results
produced by R targets package. This is provided to enable inspection of workflow
steps without running the entire workflow from the beginning. To use it, unpack
the tar achive with the command "tar -xzf _targets.tar.gz". Then, in R, the
"tar_load()" function in the R package "targets" can be used to load any
workflow step (target) defined in _targets.R
(https://github.com/joelnitta/japan_ferns_spatial_phy/blob/main/_targets.R). For
more information on the structure of the _targets folder and how to use it, see
https://github.com/ropensci/targets.

MD5 checksum: FIXME (add manually, since this can't be calculated from inside the targets workflow)

Corresponding commit in repo (https://github.com/joelnitta/japan_ferns_spatial_phy): FIXME add manually

@@

`r fs::path_file(japan_ferns_biodiv_figshare_file)` (contained in "results.zip"):
Biodiversity statistics of native, non-hybrid ferns and environmental variables
in Japan. Biodiversity metrics calculated as described in Nitta et al. 2021. 
Climatic (temperature and preciptation) variables
calculated as described for japan_climate.gpkg. Includes one row with missing
environmental data and one outlier for % apomixis that were removed prior to
spatial modeling analysis in Nitta et al. 2021.

>>>>

Recommended citation for the data: Nitta JH, Mishler BD, Iwasaki W, Ebihara A
(2022) Data from: Spatial phylogenetics of Japanese ferns: Patterns, processes,
and implications for conservation FIXME: add DOI when available

Citation for and links to publications that cite or use the data: Nitta JH,
Mishler BD, Iwasaki W, Ebihara A (2022) Spatial phylogenetics of Japanese ferns:
Patterns, processes, and implications for conservation FIXME: add journal when published

@@

- japan_climate.gpkg: Climate data in Japan downloaded from WorldClim database
- japan_deer_range.gpkg: Distribution maps of Japanese deer (Cervus nippon) in Japan
- japan_ferns_comm_full.csv: Community matrix (species x sites matrix) of native, non-hybrid ferns in Japan, full (unfiltered) dataset
- japan_ferns_inext_results.csv: Results of collection curve analysis on fern specimens in Japan
- japan_ferns_occ_summary.csv: Summary of specimen data of native, non-hybrid ferns in Japan
- japan_ferns_redundancy_by_res: Taxonomic richness, abundance, and redunancy at different spatial resolutions for native, non-hybrid ferns of Japan
- japan_ferns_shape_full.gpkg: Location of grid-cells (sites) for native, non-hybrid ferns in Japan, full (unfiltered) dataset
- japan_ferns_traits_lucid.csv: Morphological trait data of native, non-hybrid ferns in Japan
- japan_map_points.csv: Latitude and longitude of points used to produce a labeled map of Japan
- japan_map.gpkg: Map of Japan
- japan_protected_areas.gpkg: Protected areas in Japan
- testo_sundue_2016_calibrations.csv: Fossil calibration points used for phylogenetic dating analysis
- results.zip: Selected analysis results. Files include:
  - japan_ferns_biodiv.csv: Biodiversity statistics of native, non-hybrid ferns in Japan
  - japan_ferns_comm.csv: Community matrix (species x sites matrix) of native, non-hybrid ferns in Japan used for biodiversity analysis
  - japan_ferns_shape.gpkg: Location of grid-cells (sites) for native, non-hybrid ferns in Japan used for biodiversity analysis
  - japan_ferns_traits.csv: Trait matrix of native, non-hybrid ferns in Japan used for functional biodiversity analysis
  - japan_ferns_tree_dated.tre: Maximim-likelihood, ultrametric (dated) phylogeny of native, non-hybrid ferns in Japan with clades consisting of identical OTUs collapsed to polytomies
  - japan_ferns_tree_uncollapsed.tre: Maximim-likelihood, ultrametric (dated) phylogeny of native, non-hybrid ferns in Japan with clades consisting of identical OTUs not collapsed
  - japan_ferns_tree.tre: Maximim-likelihood phylogeny of native, non-hybrid ferns in Japan

@@

For full methods, see Nitta JH, Mishler BD, Iwasaki W, Ebihara A (2022) Spatial
phylogenetics of Japanese ferns: Patterns, processes, and implications for
conservation FIXME: Add journal when published

@@

@@

`r fs::path_file(japan_ferns_biodiv_figshare_file)` (contained in "results.zip"):
Biodiversity statistics of native, non-hybrid ferns and environmental variables
in Japan. Biodiversity metrics calculated as described in Nitta et al. 2022. 
Climatic (temperature and preciptation) variables
calculated as described for japan_climate.gpkg. Includes one row with missing
environmental data and one outlier for % apomixis that were removed prior to
spatial modeling analysis in Nitta et al. 2022.
